
  \SlideTitle{Books}
    \startitemize
    \item {\bf Embedded Linux Primer, Second Edition, Prentice Hall}\\
      By Christopher Hallinan, October 2010\\
      Covers a very wide range of interesting topics.
    \item {\bf Building Embedded Linux Systems, O'Reilly}\\
      By Karim Yaghmour, Jon Masters, Gilad Ben-Yossef and Philippe
      Gerum, and others
      (including Michael Opdenacker), August 2008\\
      \hyphenatedurl{http://oreilly.com/catalog/9780596529680/}
    \item {\bf Embedded Linux System Design and Development}\\
      P. Raghavan, A. Lad, S. Neelakandan, Auerbach, Dec. 2005.\\
      \hyphenatedurl{http://free-electrons.com/redirect/elsdd-book.html}\\
      Useful book covering most aspects of embedded Linux system
      development (kernel and tools).
    \stopitemize

  \SlideTitle{Web sites}
  \startitemize
  \item {\bf ELinux.org}, \hyphenatedurl{http://elinux.org}, a Wiki entirely
    dedicated to embedded Linux. Lots of topics covered: real-time,
    filesystem, multimedia, tools, hardware platforms,
    etc. Interesting to explore to discover new things.
  \item {\bf LWN}, \hyphenatedurl{http://lwn.net}, very interesting news site
    about Linux in general, and specifically about the kernel. Weekly
    newsletter, available for free after one week for non-paying
    visitors.
  \item {\bf Linux Gizmos}, \hyphenatedurl{http://linuxgizmos.com}, a news site
    about embedded Linux, mainly oriented on hardware platforms
    related news.
  \stopitemize

  \SlideTitle{International conferences}
  Useful conferences featuring embedded Linux and kernel topics
  \startitemize
  \item Embedded Linux Conference: \hyphenatedurl{http://embeddedlinuxconference.com/}\\
    Organized by the CE Linux Forum: California (San Francisco,
    Spring), in Europe (Fall).  Very interesting kernel and userspace
    topics for embedded systems developers.  Presentation slides
    freely available
  \item Linux Plumbers, \hyphenatedurl{http://linuxplumbersconf.org}\\
    Conference on the low-level plumbing of Linux: kernel, audio,
    power management, device management, multimedia, etc.
  \item FOSDEM: \hyphenatedurl{http://fosdem.org} (Brussels, February)\\
    For developers. Presentations about system development.
  \item Android Builder Summit: \hyphenatedurl{http://events.linuxfoundation.org/events/android-builders-summit}
  \item Free-electrons free conference videos on
    \hyphenatedurl{http://free-electrons.com/community/videos/conferences/}!
  \stopitemize
